### 2021-11-02 reviews/rebuttal.tex

\newenvironment{reply}
   {\medskip \noindent \begin{sf}\textbf{Reply}:\  }
   {\medskip \end{sf}}

\newcommand{\shortreply}[2][]{\medskip \noindent \begin{sf}\textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip \end{sf}}

\newcommand{\todo}{\subsection*{\textcolor{red}{To do (comment out when done)}:}}

\newcommand{\fede}[1]{\textcolor{red}{[Fede: #1]}}
%\newcommand{\av}[1]{\textcolor{blue}{[Aki: #1]}}
%\newcommand{\ami}[1]{\textcolor{brown}{[Alonzo: #1]}}
%\newcommand{\ts}[1]{\textcolor{purple}{[Tuomas: #1]}}

@@

\begin{document}

\section*{Response to the reviewers}
% General intro text goes here
We thank the editor and the reviewers for careful review of the paper and the many useful comments.
\bigskip 
\hrule
\medskip 
\section*{Associated Editor}

\paragraph{Associated Editor comment}
Please note the strong concerns of the reviewers. If you cannot implement a better projective prediction approach for complete variable selection problems, then at the very least, I would expect you to motivate why it's worth knowing about this approach; you show that it doesn't work very well.

\paragraph{Reply}
todo

@@

%\todo
%\begin{description}
%    \item [Mans] Nothing
%\end{description}

% Let's start point-by-point with Reviewer 1
\reviewersection

% Point one description 
\begin{point}
My main concern with respect to the projective predictive approach is the robustness of the results to the reference model. Apparently, you can build very different references models to the same data set: have you study the sensitivity of the results with different reference models?. You use Bayesian models as reference models and, in these cases, the determination of prior distribution is not very clear. You can build hundreds and hundreds of prior distribution: for instance in (7) you can have use standard inverted gamma priors on $\tau^2$ and $\sigma^2$ by determining the parameters of the prior in order to the prior mixture gives reasonable results about the data using the prior mixture. How can you study the robustness of your results to this important aspect?
\end{point}

\begin{reply}
We have added clarification that the reference model approach requires a sensible model, so that for example a model predicting constant output or a model predicting uncorrelated noise are not useful reference models.
A sensible reference model doesn't need to be Bayesian. The results are better with better reference models.

The sensitivity of the Bayesian models to choice of priors is well studied and there exists well-developed workflows for doing prior sensitivity analysis and other model checking \citep[see, e.g.][]{gelman2020bayesian}. In this paper the point is not the Bayesian workflow, but to analysis given a good reference model what is the importance of making the submodel inference using the decision theoretically justified version or whether other algorithms can also be improved by replacing the data with filtered prediction from the reference model. The reference models used in the examples are using widely accepted weakly informative priors and there is no prior sensitivity issues. As the same reference models are used for all algorithms, the relative comparison between different algorithms and the overall usefulness of the reference model approach is not influenced by the details of the reference models.
\end{reply}

@@

%\todo
%\begin{description}
%    \item[Mans] Clarified that we present first time how this problem should be approached in the Bayesian context.
%\end{description}

\begin{point}
Perhaps a solution to the previous problem would be to determine the reference model using frequentist MLE procedures that avoid the construction of prior distributions and use a single point prediction or, alternatively, to use the sampling distribution of MLE as a posterior distribution and take this “Bayesian” model as reference model. Do you have any experience in this line?
\end{point}

\begin{reply}
MLE is more unstable than Bayesian approach. The Bayesian approach gets the improved stability both from integration over the parameter space (instead of using a point estimate) and can further be improved by using even just weakly informative priors. We have added references that discuss merits of Bayesian approach compared to MLE. Although we think Bayesian reference models are better choice, we also assume that in large n, small p case there will be not much difference to using MLE to construct the reference model, and we believe that in what ever way the reference model has been built, if it's a good predictive model, it will be a useful reference model.
\end{reply}

\begin{point}
What if the true generator process is a mixture model, in such a way that there is not a unique solution to the minimal subset variable selection problem? In fact, how can you assure that the minimal subset variable selection problems have only one selection? I think that the algorithm described in appendix A should take into account this possibility, and the step 5 not to choose the smallest (model) that is sufficient close to the reference model's predictive utility score but to use, for instance, an Occam window, that reflects more adequately the uncertainty associated with the model selection process something that, apparently, your methodology does not consider. In fact, and even though in your examples your results in the paper were not sensitive to the specific choice of how “sufficiently close” is defined, I guess that there can be situations where this statement is not true, and more of one solution to the minimal subset variable selection problem and to the complete variable selection problem could exist.
\end{point}

\begin{reply}
The projection predictive variable selection and its properties have been extensively discussed in \citet{piironen2017comparison} and \citet{piironen2020projective}, and we refer to them for the detailed discussion on the uncertainty related to search paths. \citet{paasiniemi2018} provides illustrations how this uncertainty can be communicated to the users. When there are correlating variables that have exactly the same amount of information, the minimal set is not unique. In this paper, we focused on the average performance of the minimal set, but when analysing a single dataset, we recommend the approaches presented in \citet{paasiniemi2018} to analyse alternative possible variable sets.
\end{reply}

\begin{point}
In most of real situations, we have an M-open problem (particularly in big data problems) where the true generator mechanism is too complex and it is not included in the family of considered models. What would be the performance of your methodology if the reference model is far from the true generator process? How can you detect these situations?
\end{point}

\begin{reply}
We assume that all models are wrong. Analysing model misspecification is well studied in Bayesian literature and there are plenty of methods available for model checking \citep[see, e.g.][]{gelman2020bayesian}. The reference model approach assumes we have first made the best possible model, following all the best practices for Bayesian model building \citep{gelman2020bayesian}. Even a misspecifed model that would introduce some bias can reduce the variance so that the variable selection is improved. 
\end{reply}

\begin{point} \label{q5}
In big data problems with n << p and the explanatory variables are weakly related (in such a way that the number of significant principal components is large), how do you build a reference model? Is it possible?
\end{point}

\begin{reply}
See \citet{piironen2020projective}.
\end{reply}

\begin{point}
The same question that \ref{q5} but if n is small and your data have not power to discriminate between two alternative reference models.
\end{point}

\begin{reply}
The usual Bayesian workflow \citep{gelman2020bayesian} states that if there is uncertainty about which model then we integrate over the model space or create a continuous super model that includes the alternative models as special cases.
\end{reply}

%%% SOME OF THE MINOR REQUEST
\section*{Reviewer 1 - Minor comments}

\begin{point}
Section 3.1: you say that in this simulation you use a Bayesian stepwise forward selection procedure. Is this really the case? In your description of the procedure in page
6 you exclude (and not include variables) in this step of the algorithm. In my view, this procedure is a Bayesian stepwise backward selection procedure.
\end{point}

\begin{reply}
Thanks for pointing out the typo. We fixed it in the new version of the paper.
\end{reply}

\begin{point}
In the Bayesian stepwise selection procedures of section 3.1 you use posterior pvalues to exclude variables, and you exclude the variable with the highest Bayesian p- value. Shouldn't you take into account whether the value of the pvalue is large or small? Shouldn't you calibrate these pvalues?
\end{point}

\begin{reply}
\fede{There is not need of calibration of the pvalues since they are used only to select the "worse" predictor. Then the variable is excluded or not looking at the predictive performance of the reduced model compared to the not-reduced one. In such a way, the posterior pvalues matter only for their ordering and not for their magnitude.}
\end{reply}

\begin{point}
Section 3.1 steplm procedure: Why have you chosen the AIC criterion which, as it is well-known tend to select non-parsimonious models? Have you tried to use the BIC criterion instead? In my experience, this criterion tend to select more parsimonious models and in a M Complete approach, it is usually consistent.
\end{point}

\begin{reply}
We used AIC because reference X was using AIC. The goal of the paper was not to compare all possible information criteria. We made choices to keep the paper within reasonable length. Based on the results, we assume that variable selection using any *IC approach will benefit from using a reference model. 
\end{reply}

\begin{point}
Section 4.1, page 8, line 38: $\text{elpd}_\text{base}$ should be $\text{elpd}_\text{best}$
\end{point}

\begin{reply}
Thanks for pointing out the typo. We fixed it in the new version of the paper.
\end{reply}

\begin{point}
How is calculated the probability used in the stopping rule (2)? Using the reference model?
\end{point}

\begin{reply}\label{reply:stopping}
\fede{At each iteration, the best model is selected via the default stopping rule implemented the \texttt{R}-package \texttt{projpred}. For details, see \citet{piironen2020projective} for details. In few words, the predictive performance is evaluated via cross-validation both for the reference model and the submodels using the log-predictive density (lpd) score. The obtained lpd samples are used to estimate that probability under normality assumption.}
\end{reply}

\begin{point}
It is not very exigent in (2) to impose that $\text{elpd}_i-\text{elpd}_\text{best}>0$? Perhaps you should consider other limits similar to those used in Bayes factors (Kass and Raftery, 1995) and not to choose only on solution but to explore other possible solutions in the spirit of Occam’s window
\end{point}

\begin{reply}
\fede{The above condition comes from the implementation of the projection predictive approach \citet{piironen2020projective} in the \texttt{R}-package \texttt{projpred}. The fact that the algorithm is based on the probability of that condition and not on the condition itself make it not that exigent.}
\end{reply}

\begin{point}
Section 4.1: It is no clear how the value of $\alpha$ should be chosen. $\alpha= 0.16$ is a magic number and a more thoroughly discussion of the influence of this value should be provided.
\end{point}

\begin{reply}
\fede{The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}. One possible standard way to proceed, but not guaranteed to be the best in any case, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score. For further details see \ref{reply:stopping} and \citet{piironen2020projective}.}
\end{reply}

\begin{point}
Section 4.1, line 50 “expect” should be “except”
\end{point}

\begin{reply}
Thanks for pointing out the typo. We fixed it in the new version of the paper.
\end{reply}

\reviewersection

No comments provided.

\reviewersection

\begin{point}
Although main articles related to the use of the reference model approach in the model selection are mentioned, the motivation of the study in relation to the literature is missing in the Introduction. The given discussion of the existing literature supports the idea that the reference models have been used in Bayesian and non-Bayesian contexts. However, why do we need the proposed approach in the article is missing. Full motivation is given in Section 2. However, it needs to be briefly mentioned in the Introduction as well to motivate the reader to keep reading. In addition, instead of pointing to the references, please give a brief critique of them.
\end{point}

\begin{reply}
todo
\end{reply}

\begin{point}
Please include the computational cost of compared approaches in Section 2.1. 
\end{point}

\begin{reply}
todo
\end{reply}

\begin{point}
Please add a brief summary of the results you obtained in Section 3 and the main message you infer from these results before moving onto Section 4.
\end{point}

\begin{reply}
todo
\end{reply}

\begin{point}
Please mention the availability of the R codes to reproduce the results under each section as well.
\end{point}

\begin{reply}
Thank you for the feedback, we mentioned the availability of the R codes under each section in the new version of the paper.
\end{reply}

\bibliographystyle{abbrvnat}
\bibliography{rebuttal}

\end{document}
